Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-03-25 eg6-letters/incoherent/March2019_Updated_docs_for_LZ15969_Hattawy/publication_version/incoherent_prl.tex
some cleaning for the directory after being re-submitted

In the final sample, the exclusivity of the incoherent DVCS events was ensured 
by imposing a series of constraints based on the four-momentum conservation in 
the reaction $ep\rightarrow e'p'\gamma$.  These kinematical variables are: the 
coplanarity angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and 
($\gamma^*$,$p'$) planes, the missing energy, mass, and transverse momentum of 
the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass squared of the $e'p'$ 
system, and the angle $\theta$ between the measured photon and the missing 
momentum of the $e'p'$ system. The experimental distributions for the most relevant 
exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
Fermi motion of the nucleons in the helium nucleus, the cuts indicated by the dashed lines
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}

\end{figure}
\begin{figure}[h!]
\hspace{-0.45cm}
\includegraphics[width=9.0cm]{figs/Q2_xB_t_InCoh.pdf}
\caption{Incoherent DVCS event distributions for $Q^{2}$ as a function of 
$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the exclusivity 
cuts.}
\label{fig:kin-coverage}
\end{figure}

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
contributions to systematic uncertainties on these fits are from the choice of 
the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical uncertainties.

>>>>

In the final sample, the exclusivity of the incoherent DVCS events was ensured 
by imposing a series of constraints based on the four-momentum conservation in 
the reaction $ep\rightarrow e'p'\gamma$.  These kinematical variables are: the 
coplanarity angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and 
($\gamma^*$,$p'$) planes, the missing energy, mass, and transverse momentum of 
the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass squared of the $e'p'$ 
system, and the angle $\theta$ between the measured photon and the missing 
momentum of the $e'p'$ system. The experimental distributions for the most relevant 
exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
Fermi motion of the nucleons in the helium nucleus, the cuts indicated by the dashed lines
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At the end of this selection 
process, about 30k events passed all the requirements.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing mass squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}
\end{figure}

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{incoherent_ALU_phi_t.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$ for different $t$ 
   bins. The error bars represent the statistical uncertainties. The gray 
   bands represent the systematic uncertainties, including the normalization 
   uncertainties. The black curves are the results of our fits with the form 
   $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $t$ (integrated over the full $Q^{2}$ and $x_{B}$ ranges).  
The curves on the plots are fits of the form $\frac{a_{0}~\sin(\phi)}{1+ 
a_{1}~\cos(\phi)}$. The main contributions to systematic uncertainties on these fits are from the choice of 
the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical uncertainities.
